Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse

### 2014-12-17 Model.tex
Game tree diagrams
Clearer emulated-simulated figure

Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation) even at the subgame level. Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

\begin{figure}[H]
\begin{adjustbox}{center}
\subfloat[Women]{\includegraphics[width=0.43\paperwidth]{figures/simple_game_tree}}
\end{adjustbox}
\caption{Simmplified game tree.}

@@

>>>>

Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level. Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.43\paperwidth]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree.}

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.43\paperwidth]{figures/tree_zoom}
\end{adjustbox}
\caption{Detail view of a single game tree branch.}

\label{fig:zoom_tree}
\end{figure}
